### 2024-07-18 evaluating-prediction-accuracy.qmd
20240718 - update Hyndman book edition

The estimates of prediction accuracy described in this section are intended to be scale-*independent* (unit-free) so the accuracy estimates can be compared across measures with different scales or across data sets [@Hyndman2018].

@@

Mean absolute scaled error (MASE) is described by [@Hyndman2018].
Values closer to zero reflect greater accuracy.

>>>>

The estimates of prediction accuracy described in this section are intended to be scale-*independent* (unit-free) so the accuracy estimates can be compared across measures with different scales or across data sets [@Hyndman2021].

@@

Mean absolute scaled error (MASE) is described by [@Hyndman2021].
Values closer to zero reflect greater accuracy.
